### 2016-12-21 Plos-one-manuscript/latex/manuscript.tex
working

Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
As air is an expansible fluid, this pocket of air expands due to the weight of the liquid pulling on it.
Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
At larger volumes this effect is more pronounced resulting in the volume measured being greater then the amount of liquid pulled into the syringe.
We remedied this by creating a new scale to account for the expansion.
The scale is printed on a transparency sheet and is pasted on the syringe for accurate measurements.

@@

A small amount of parrifin wax is applyed to the screw to prevent slop from causing the set point to drift after each acuation.
This was effective in preventing drift.
The nut is sunk in to the hex inset in the body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of the 1 mL syringe for the 30-300 uL configuration.
Springs are placed inside the 3 mL syringe for the 100-1000 mL configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.

>>>>

Our pipette uses the air-displacement design, where a pocket of air is used to draw liquid into the pipette.
As air is an compressible fluid, this pocket of air grows due to the weight of the liquid pulling on it.
Due to this effect the graduations on the syringe are not accurate, as they are designed for measuring liquid within the syringe.
At larger volumes this effect is more pronounced resulting in the volume measured being greater then the amount of liquid pulled into the syringe.
We remedied this by creating a new scale to account for the expansion.
The scale is printed on a transparency sheet and is pasted on the syringe for accurate measurements.

@@

A small amount of parrifin wax is applyed to the screw to prevent slop from causeing the set point to drift after each acuation.
The nut is sunk in to the hex inset in the body part.
The bolt is threaded in from the top of the body into the nut.
Springs and washers are threaded onto the plunger of the 1 mL syringe for the 30-300 uL configuration.
Springs are placed inside the 3 mL syringe for the 100-1000 mL configuration.
The plunger part is inserted in the body and the syringe assembly is pushed in and locked from the syringe flanges to the body part to complete assembly.
